Handling missing data in smartphone location logs

### 2017-11-30 thesisReport.Rmd
bookdownified the thesis

---
title: 'Handling missing data in smartphone location logs'
author: "Boaz Sobrado"
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography:
  - thesisGPS.bib
  - rReferences.bib
output:
  rmarkdown::pdf_document:
    citation_package: natbib
    fig_caption: yes        
    includes:  
      in_header: tp2.tex

@@

# A concrete example

@@

## Methods

>>>>

---
title: 'Handling missing data in smartphone location logs'
author: "Boaz Sobrado"
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography:
  - thesisGPS.bib
  - rReferences.bib
biblio-style: apalike
link-citations: yes
output:
  bookdown::pdf_book:
    citation_package: natbib
    fig_caption: yes        
    includes:  
      in_header: tp2.tex

@@

## A concrete example

@@

# Methods
